---
title: "Graphs"
---

```{r setup, include=FALSE, cache=TRUE}
source('functions.R')
library(targets)
tar_load_everything(strict=FALSE)
final_data <- SharedData$new(covid_presentation_data)
```


First is a scatter plot showing with color the percentage of healthcare staff currently (as of the week ending  `r max(covid_data$'Week Ending', na.rm=TRUE)`) fully vaccinated for covid, with the horizontal axis showing the percentage of residents fully vaccinated and the vertical axis showing the number of residents who died from covid, normalized over the number of residents through time (these data all come directly from <https://data.cms.gov/covid-19/covid-19-nursing-home-data>). There are histograms after that for counts. You can use the sliders and checkboxes below to filter facilities and the graphs will automatically update. Clicking on any point will show detail on the facility.

## Scatter plot of nursing home covid deaths vs. resident vaccination rates


{{< include filter.qmd >}}


```{r, echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
library(leaflet)
my_palette <- colorNumeric( "viridis", domain=seq(from=0, to=1, length.out=101), reverse=TRUE)(seq(from=0, to=1, length.out=101))

library(plotly)
fig <- plot_ly(final_data, x = ~`ResidentFullPercent`, y = ~`Total Resident Covid Deaths Per 1,000 Residents`, color = ~`Current Healthcare Personnel Up to Date with Covid Vaccines`, colors=my_palette, type = 'scatter', mode = 'markers', text = ~PopupLabel, hoverinfo = 'text', marker = list(size = 10, opacity = 0.8)) |> layout(showlegend = FALSE) |> hide_colorbar() 
fig <- layout(fig, yaxis = list(type = "log"), xaxis = list(title = 'Percentage of nursing home residents fully vaccinated'))
fig <- layout(fig, yaxis = list(title = 'Total resident covid deaths per 1,000 residents'))
fig
```

::: {.callout-note}

Some of these rates look remarkably high. From the FAQ at <https://data.cms.gov/covid-19/covid-19-nursing-home-data>:

How can there be more confirmed COVID-19 cases than beds in a nursing home?

The nursing home data posted reflects cumulative cases and deaths of COVID-19 reported in a facility. A nursing home may report more confirmed COVID-19 cases than beds because they may encounter a large number of admissions and discharges of residents with COVID-19, resulting in more cumulative cases of COVID-19 over time than the number of beds at any one time.

This may also be due to a data entry error on the part of the facility – for example, a nursing home may be entering cumulative numbers of confirmed COVID-19 cases in a field where the facility should only be entering the number of new cases.

:::


---

Next are a histogram showing the counts of nursing homes with different proportions of healthcare staff or residents fully vaccinated fully vaccinated for covid.



## Nursing home healthcare staff full vaccination rates

```{r, echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}

fig <- plot_ly(final_data, x=~StaffFullPercent) |> add_histogram() |> layout(showlegend = FALSE) |> hide_colorbar() |> layout(xaxis = list(title = 'Percentage of nursing home healthcare staff fully vaccinated')) |> layout(yaxis = list(title = 'Count of nursing homes'))

fig
```

## Nursing home healthcare staff who have ever received a covid vaccine

```{r, echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}

fig <- plot_ly(final_data, x=~StaffEverVaxPercent) |> add_histogram() |> layout(showlegend = FALSE) |> hide_colorbar() |> layout(xaxis = list(title = 'Percentage of nursing home healthcare staff ever vaccinated')) |> layout(yaxis = list(title = 'Count of nursing homes'))

fig
```

## Nursing home resident full vaccination rates

```{r, echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}

fig <- plot_ly(final_data, x=~ResidentFullPercent) |> add_histogram() |> layout(showlegend = FALSE) |> hide_colorbar() |> layout(xaxis = list(title = 'Percentage of nursing home residents fully vaccinated')) |> layout(yaxis = list(title = 'Count of nursing homes'))

fig
```

