---
title: "Nursing home covid"
---

```{r setup, include=FALSE, cache=TRUE}
source('functions.R')
library(targets)
tar_load_everything(strict=FALSE)
final_data <- SharedData$new(covid_presentation_data)
```


The US Centers for Medicare and Medicaid Services puts out a dataset of covid incidence, deaths, and vaccination at `r nrow(covid_cleaned)` US nursing homes. The data are available at <https://data.cms.gov/covid-19/covid-19-nursing-home-data>. It has info on individual nursing homes, but it can be a little hard to use. I am making it more usable here, trying to make it easier for folks to see how people in nursing homes are being cared for. This uses federal data from the week ending `r max(covid_data$'Week Ending', na.rm=TRUE)`. 

The tabs above have different views of the data. **If you want to look at detail on a particular facility, it is probably easiest to use the [map](map.html) or [table](table.html) pages**. Some quick summaries:

* `r nrow(subset(covid_presentation_data, StaffFullPercent==0))` nursing homes have zero healthcare staff fully up to date on covid vaccines.
* `r nrow(subset(covid_presentation_data, StaffFullPercent==100))` nursing homes have all healthcare staff fully up to date on covid vaccines.
* `r round(100*sum(covid_geo$"Number of Healthcare Personnel Eligible to Work in this Facility for At Least 1 Day This Week Up to Date with COVID-19 Vaccines", na.rm=TRUE)/sum(covid_geo$"Number of All Healthcare Personnel Eligible to Work in this Facility for At Least 1 Day This Week", na.rm=TRUE))`% of nursing home healthcare staff nationwide are fully up to date on covid vaccines.

* `r nrow(subset(covid_presentation_data, ResidentFullPercent==0))` nursing homes have zero residents fully up to date on covid vaccines.
* `r nrow(subset(covid_presentation_data, ResidentFullPercent==100))` nursing homes have all residents fully up to date on covid vaccines.
* **Only `r round(100*sum(covid_presentation_data$'Beds Occupied' * covid_presentation_data$'Current Residents Up to Date with Covid Vaccines', na.rm=TRUE)/sum(covid_presentation_data$'Beds Occupied', na.rm=TRUE), 1)`% of nursing home residents are fully up to date on covid vaccines**.

### Current inferred covid infection rates

This is based on dividing the weekly number of cases in healthcare staff or residents by the number in that facility over the week. There may be a lot of biases here: for example, if not every resident and staff member is tested every week, especially if some facilities never test or report, then the rate will be too low. There may also be issues if, say, a resident or staff member moves between facilities -- they could appear in the data twice.

```{r, echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
fig <- plot_ly(covid_by_time_US_total, x = ~`Week Ending`, y = ~`weekly_resident_covid_percentage`, type = 'scatter', mode = 'lines+markers', name="Residents") |> add_trace(y = ~weekly_staff_covid_percentage, name = 'Staff', mode = 'lines+markers') |> layout(yaxis = list(title = "Inferred percentage with covid"), xaxis = list(title = 'Week Ending')) |> layout(legend = list(x = 0.1, y = 0.9))
fig
```

### Map of covid incidence
```{r, echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
current <- subset(covid_by_time, `Week Ending`==max(covid_by_time$`Week Ending`))
current$state <- current$State

plot_usmap(data=current, values="weekly_resident_covid_percentage") + theme(legend.position="top") + scale_fill_viridis(name=paste0("Percent of nursing home residents with covid\n(Week ending ", unique(current$`Week Ending`), ")"), rescaler = function(x, to = c(0, 1), from = NULL) {
    ifelse(x<3.5, 
           scales::rescale(x,
                           to = to,
                           from = c(min(x, na.rm = TRUE), 3.5)),
           1)})
		   

plot_usmap(data=current, values="weekly_staff_covid_percentage") + theme(legend.position="top") + scale_fill_viridis(name=paste0("Percent of nursing home staff with covid\n(Week ending ", unique(current$`Week Ending`), ")"), rescaler = function(x, to = c(0, 1), from = NULL) {
    ifelse(x<3.5, 
           scales::rescale(x,
                           to = to,
                           from = c(min(x, na.rm = TRUE), 3.5)),
           1)})
```

### Map of vaccination status
```{r, echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}

plot_usmap(data=current, values="weekly_resident_vax_percentage") + theme(legend.position="top") + scale_fill_viridis(name=paste0("Percent of nursing home residents fully vaccinated\n(Week ending ", unique(current$`Week Ending`), ")"), option="H")
		   

plot_usmap(data=current, values="weekly_staff_vax_percentage") + theme(legend.position="top") + scale_fill_viridis(name=paste0("Percent of nursing home staff fully_vaccinated\n(Week ending ", unique(current$`Week Ending`), ")"), option="H")
```

